A Triangle Mesh Approach to Painting

### 2014-04-21 template.tex
Moving figures, added missing references.

\subsection{Converting Strokes to Contours}
A set of contours define the outline of a stroke. For simply connected strokes, those without holes, 
one contour describes the whole stroke. However, strokes with holes, such as a circle or 
figure-eight, will have more than one contour.
Converting a user's mouse motion into a set of contours requires two steps.
First, the user's mouse movements are captured by a set of polygons which can be
rendered to yield a rasterized version of the stroke.
Second, to obtain the contours the stroke is rasterized in black and marching squares~\cite{XXX}
is used to extract iso-contours of 50\% gray. This returns a very dense set of points 
which we reduce through a pruning process to
get a sparse but accurate representation of the contour.

@@

We utilized Jonathan Shewchuk's Triangle library~\cite{XXX} to perform constrained Delaunay triangulations
on the given set of points and boundaries. The library outputs a mesh that
approximately represents the drawn stroke.

@@

Again, using marching squares these contours are extracted and then pruned. The boundaries and points
derived from the contours are given to Triangle and a mesh is returned. This mesh represents the soft
stroke where no triangle crosses the boundary between the soft and hard regions
of the stroke. Points on the contour of the inner stroke will have color arcs with the stroke color,
while the points on the contour of the outer stroke will have transparent color arcs. This gives
all triangles connecting the inner and outer strokes a linear gradient (again see Figure~\ref{softarcs}).
Figure~\ref{fig:rastertotriangles} shows the process of triangulating both hard and soft strokes.

@@

\begin{figure}
    \centering
        \includegraphics[width=.5\textwidth]{images/grid}
    \caption{An example of how TrianglePainter determines which triangles to save and which to retriangulate. Blue
    lines represent the boundaries of old strokes, orange lines are the boundaries of the new stroke, red lines are
    the triangles that will be reused, and purple lines define the area that needs to be retriangulated. The purple
    lines are edges of triangles that intersect the new stroke. Since they interesect the new stroke they are no
    longer valid and must be retriangulated. All other triangles on the canvas can be reused.}
    \label{fig:modified}
\end{figure}

\section{Discussion and Results}
Paintings made with TrianglePainter can be seen in Figures~\ref{fig:face}, \ref{fig:rainbow}, \ref{fig:stop} and \ref{fig:boxes}.  Here we first consider how the complexity of the algorithm grows both in time and geometry.
The results from this analysis and our experience with TrianglePainter have lead to a number of observations.

@@

@@

\begin{figure*}
    \centering
        \includegraphics[width=0.49\textwidth]{images/rainbow2}
        % \includegraphics[width=0.49\textwidth]{images/facezoomtriangles}
    \caption{An example of soft strokes}
    \label{fig:rainbow}
\end{figure*}

>>>>

\subsection{Converting Strokes to Contours}
A set of contours define the outline of a stroke. For simply connected strokes, those without holes, 
one contour describes the whole stroke. However, strokes with holes, such as a circle or 
figure-eight, will have more than one contour.
Converting a user's mouse motion into a set of contours requires two steps.
First, the user's mouse movements are captured by a set of polygons which can be
rendered to yield a rasterized version of the stroke.
Second, to obtain the contours the stroke is rasterized in black and marching squares~\cite{lorensen1987}
is used to extract iso-contours of 50\% gray. This returns a very dense set of points 
which we reduce through a pruning process to
get a sparse but accurate representation of the contour.

@@

We utilized Jonathan Shewchuk's Triangle library~\cite{shewchuk2002} to perform constrained Delaunay triangulations
on the given set of points and boundaries. The library outputs a mesh that
approximately represents the drawn stroke.

@@

Again, using marching squares these contours are extracted and then pruned. The boundaries and points
derived from the contours are given to Triangle and a mesh is returned. This mesh represents the soft
stroke where no triangle crosses the boundary between the soft and hard regions
of the stroke. Points on the contour of the inner stroke will have color arcs with the stroke color,
while the points on the contour of the outer stroke will have transparent color arcs. This gives
all triangles connecting the inner and outer strokes a linear gradient (again see Figure~\ref{fig:softarcs}).
Figure~\ref{fig:rastertotriangles} shows the process of triangulating both hard and soft strokes.

@@

\section{Discussion and Results}
Paintings made with TrianglePainter can be seen in Figures~\ref{fig:face}, \ref{fig:teaser}, \ref{fig:stop} and \ref{fig:boxes}.  Here we first consider how the complexity of the algorithm grows both in time and geometry.
The results from this analysis and our experience with TrianglePainter have lead to a number of observations.

@@

\begin{figure}
    \centering
        \includegraphics[width=\columnwidth]{images/grid}
    \caption{An example of how TrianglePainter determines which triangles to save and which to retriangulate. Blue
    lines represent the boundaries of old strokes, orange lines are the boundaries of the new stroke, red lines are
    the triangles that will be reused, and purple lines define the area that needs to be retriangulated. The purple
    lines are edges of triangles that intersect the new stroke. Since they interesect the new stroke they are no
    longer valid and must be retriangulated. All other triangles on the canvas can be reused.}
    \label{fig:modified}
\end{figure}

@@
